Vector Representations of Linguistic Communities and Associated Models

### 2022-09-19 paper/paper1.tex
changes from last round of reviews

\date{}

\begin{document}
\maketitle
\begin{abstract}
  Community-level linguistic variation is a core concept in sociolinguistics.
  % but more tools are needed to study variation from a computational perspective.
  In this paper, we use computational methods to investigate the degree to which  
  linguistic variation corresponds with social connections between communities.
  Technically, we use conditional language models to learn vector representations
  for 510 online communities.
  We find that they are highly correlated with a social network-based 
  representation that does not use any linguistic input.
\end{abstract}

@@

Variation is an important object of study in sociolinguistics,
and is naturally amenable to computational analysis \citep{Nguyen2016}.
Most previous computational work on linguistic variation 
has considered variation at the level of macro-social categories, such as gender
\citep{Burger2011,Ciot2013,Bamman2014}, age \citep{Nguyen2013}, and
geographic location \citep{Eisenstein2010,Bamman2014a}.%
\footnote{Recent exceptions are \citet{DelTredici2017} who use a modified
skip-gram model to show that lexical semantic variation occurs even across 
different communities organised around the same topic and 
\citet{Lucy2021}, who use contextualised word representations to
investigate community-level variation in word sense distributions.}
In the present work, we investigate linguistic variation
in online communities on the social media website Reddit. 
This contrasts with previous work: we investigate variation across 
speech communities, rather than macro-social categories.

@@

For this purpose, we introduce (\cref{sec:cclm}) various
Community-Conditioned Language Models (CCLMs for short). These models
are conditioned on a vector representation (or embedding), which
varies for each community. Hence, they learn \emph{community
  embeddings}.  Even though we report which architectures make best use
of the community information, our primary purpose is not to improve models in
terms of perplexity, but rather we want to extract the best set of
community embeddings and test how the resulting embeddings
predict the social structure of subreddits. Technically, we test
the correlation with a social network-based representation of
communities (\cref{sec:embedding-analysis}).

@@

We experiment with two kinds of model architecture: a simple
unidirectional LSTM \citep{Hochreiter1997} and a Transformer
\citep{Vaswani2017}. Although Transformer-based language models are considered
state-of-the-art, they achieve dominance partly thanks to the
availability of very large data sets \citep[e.g.,][]{Devlin2019,Brown2020},
which are not available to us.\footnote{Fine-tuning existing models
  is not compatible with our methodology, because we fundamentally
  change the structure of the network by concatenating
  community embeddings with hidden states at various levels.} Thus the LSTM is a worthy model to test for us.

@@

In the CCLMs, we add a \emph{community embedding} parameter.
This parameter is concatenated (at each time step) with the hidden layer of the
sequence encoder, at some layer $l_c \leq n$, and passed through a
linear layer which projects the resulting vector back to the original
hidden layer size.  For $l_c = n$, the output of this linear layer is
passed directly to the softmax function, just as the final hidden
layer of the sequence encoder is in other models.  For $l_c=0$, the
community embedding is concatenated with the token embedding.  For
this reason, we set the hidden size of the sequence encoder and the
size of the token embedding to be equal for all models.

@@

The models use a vocabulary of \num{40000} tokens (including a special
out-of-vocabulary token), consisting of the most frequent tokens
across all communities.

We trained the models on a simple 
auto-regressive language modeling task with cross-entropy loss.  Because
the transformer operates on all tokens in the sequence at once, the
inputs to the model were masked and incrementally un-masked.
We used the AdamW
\citep{Loshchilov2019} optimisation algorithm, with an initial
learning rate of \num{0.001}, with no extra control on the decay
of learning rate.
%
The batch size was \num{256} and the maximum sequence length set to
\num{64} tokens, truncating longer messages (16.8\% of messages were
longer than \num{64} tokens).  During training, a dropout rate of
$0.1$ was applied between encoder layers and after each linear layer.

All experiments use models with \num{3} encoder layers,
each with hidden (and token embedding) size of \num{256}. 
The transformer models had \num{8} attention heads per layer.\footnote{
  This number of attention heads was chosen to give the LSTM and transformer
  models a comparable number of parameters 
  (\num{22171203} and \num{21779523}, respectively).}
The conditional models were given a community embedding with \num{16} dimensions. 
We experimented with every possible value for $l_c$ in a three-layer model ($l_c\in\{0,1,2,3\}$).

@@

\section{CCLM Performance}

@@

We also consider the average information gain per token of the CCLM over its baseline
un-conditioned counterpart, with the same sequence encoder architecture.
For a given message, information gain is defined as the difference
between the cross-entropy of the unconditioned model and the conditioned model:
\[H_{\mathrm{LM}}(m) - H_{\mathrm{CCLM}}(m)\]
For a set of messages, $M$, we consider the average information gain
in exponential space (as a ratio of perplexities):
\[\IG_M = \frac{e^{\avg_{m \in M}(H_{\mathrm{LM}}(m))}}{e^{\avg_{m \in M}(H_{\mathrm{CCLM}}(m))}}\]
\[\IG_M = {e^{\avg_{m \in M}(H_{\mathrm{LM}}(m) - H_{\mathrm{CCLM}}(m))}}\]
%
Unsurprisingly, the conditioned models mostly have lower perplexity 
than their respective unconditioned baseline models, 
meaning information gain above one (\cref{tab:model-results}).
While the absolute performance ($\Ppl_{M_j}$) of the LSTM models is better,
the best transformer models have somewhat higher information gain
than their LSTM counterparts.

The effect of $l_c$, the depth of the community embedding,
is also different across architectures.
For the LSTM encoder, 
the best model concatenates the community embedding after the first encoder layer ($l_c=1$),
but all of the conditioned models perform similarly well.
For the transformer, the best model incorporates the community information
first, concatenating it directly to the word vectors ($l_c=0$).
It performs similarly to the model that only integrates the community information
after all all the transformer layers ($l_c=3$),
but the two middle-layer models actually perform worse than the unconditioned model
(with $\IG_M < 1$).

We additionally observe that the best LSTM model achieves better
performance than the best Transformer model. This partly contradicts
the fact that Transformer-based models are the ones used in
state-of-the art models for mainstream tasks. We propose that the
cause is that we are training all models from scratch on a relatively
small dataset. In this situation, the relatively smaller number of
parameters of the LSTM means that it can generalise better than the
Transformer.

@@

We also consider performance stratified by community; that is,
$\Ppl_{M_j}$ and $\IG_{M_j}$, 
where $M_j$ is the set of messages originating from community $c_j$ 
(\cref{fig:comm-stratified-box}).
We observe a lot of variation in baseline perplexity
across communities, with $\Ppl_{M_j}$ ranging from \num{3.67} to
\num{93.58} for the best conditional LSTM model 
(\cref{fig:comm-stratified-box}; also see supplementary materials for perplexity by community). 
The conditioned models also perform differently across different communities---%
even among the best models, some communities have $\IG_{M_j} < 1$,
meaning that the CCLM performs worse than the unconditioned baseline for 
messages from that community.
For other communities $\IG_{M_j}$ is much higher, meaning that the CCLM performs better  
(\cref{fig:comm-stratified-box}).\footnote{
  Some of the communities with consistently high $IG_{M_j}$ 
  across all models are primarily non-English, 
  but surprisingly, not the three most extreme
  outliers. There are \subreddit{counting}, \subreddit{friendsafari}, and \subreddit{Fireteams}, 
  the later two of which are places where people coordinate to play video games
  together. The messages in these communites adhere to highly regular formats, 
  which are presumably conventional to the community.}
%
%The variation in information gain across communities is not 
%related to perplexity, however (\cref{fig:ppl-info-gain}).

@@

In this section we investigate the degree to which CCLM community
embeddings correlate with the community-member relationship on Reddit.

To this end, we compare the CCLM-learned community
embeddings\footnote{
  In this section, we only consider the embeddings from 
  the \emph{best} (highest information gain) CCLM from each architecture family; 
  that is, the LSTM with $l_c=1$ and the Transformer with $l_c=0$, however we
  observed similar results for other values of $l_c$.}
with the community embedding created by \citet{Kumar2018},\footnote{
  Available at \url{https://snap.stanford.edu/data/web-RedditEmbeddings.html}}
which were generated using using a negative-sampling optimization
algorithm, with the message author-community co-occurrence matrix as ground
truth, using data from January 2014 to April 2017.
We refer the reader
to \citet{Kumar2018}
for details, but the important point is that no linguistic
information is used to create these embeddings: they only reflect the social
relationship between communities, via 
the user-community membership relation. In contrast, CCLM community embeddings depend in no
way on which user is the author of any given message: we only use the
contents of messages, not authorship data.
%

@@

We consider communities from three different selection criteria: 
Those with high linguistic \emph{and} social similarity 
(where the sum of the two is highest),
those with high linguistic and low social similarity
(where social similarity is below the median and linguistic similarity is highest), and
those with low linguistic and high social similarity
(where linguistic similarity is below these median and linguistic similarity is highest).\footnote{We use the LSTM ($l_c=1$) community vectors for these purposes, 
  but results attain with the best transformer model.}\footnote{Median similarity
  among pairs of communities was \num{0.177} for the social embedding
  and \num{0.010} and \num{0.012} for the LSTM and transformer
  linguistic embeddings, respectively.}
We do not consider pairs of communities that are different in both ways,
since these don't offer much in the way of understanding the respective embeddings.

Unsuprisingly, the first category (\cref{fig:embedding-differences-examples}, left) yields communities that are qualitatively very similar. 
The \subreddit{SSBPM} and \subreddit{darksouls} communities are focused
around discussion of a particular videogame, and are paired
with communities that discuss a variation of the same game.
The \subreddit{amiugly} and \subreddit{Rateme} communities are both 
forums where the posts are selfies and the comments are mostly 
comments on the person's appearance.
The two communities paired with \subreddit{reddevils} are 
likewise comprised of fans of a particular English football club.
That the three football club communities are so closely related points
to an important point about the social embedding: because of the way
it was trained, it does not have to be the case that communities with
a similar representation have a high overlap in membership,
but rather that members from the first community look similar
to members from the second community in terms of their \emph{overall}
community membership profile.

@@

The analysis shows positive correlation for both the LSTM ($r=0.438$)
and transformer ($r=0.452$) linguistic embeddings.\footnote{ By
  comparison, the correlation between the two linguistic embeddings is
  \num{0.759}.}  The correlations are significant with $p<0.001$ in
all cases.  However, we note that the number of pairs grows with the
square of the number of communities (with 510 communities, we have
129795) pairs), meaning that standard statistical tests on Pearson
correlation will assure us of statistical significance in all but the
weakest of correlations. A further flaw is that the data points in
\(C\) are \emph{not} distributed independently---far from it in fact,
since each data point is generated from \num{2} of \num{510}
independent variables. We consider this last flaw fatal, and take a
different approach for computing the correlation between community
embeddings in the next section.

@@

There are several recent studies that aim to measure \emph{linguistic distinctiveness}
at the level of speech community \citep{OConnor2010,Zhang2018,Lucy2021}, 
which is an possible interpretation of the community-stratified information gain 
of the CCLM over its unconditioned counterpart (\cref{sec:ig}). 
Whereas the metrics in previous work are based on lexical frequency
(and in the case of \citet{Lucy2021}, word sense distributions),
CCLM information gain is capable of capturing 
distinctiveness at multiple levels of linguistic analysis. 
However, further work is needed to
investigate exactly what kinds of variation are captured.

@@

For LSTM models, the perplexity per word, averaged over
messages from all communities, was between \num{66.01} and \num{66.35}
(with \num{68.74} for the unconditioned model).
For transformer models, it varies a bit more, between \num{75.66} and \num{83.53},
but this seems to be mainly due to the poor performance of the models where
the community embedding is inserted between transformer layers
($l_c=2$ and $3$ both test above the unconditioned transformer's 
average perplexity of \num{79.13}).
This could be due to the community embedding and linear layers
interrupting the delicate layer normalisation between transformer encoder layers.

The pattern of information gain by community is similar across
architectures;  communities that benefit most from the conditioned
model behave that way for both the LSTM and transformer.  However,
there are some differences.  For example, many of the communities with the biggest 
difference in information gain between the $l_c=0$ and $l_c=3$ LSTMs 
are organised around trading collectables or organising virtual meetups
(e.g.,
%\subreddit{friendsafari},
%\subreddit{Fireteams},
%\subreddit{RandomActsOfGaming},
%\subreddit{randomactsofcsgo},
\subreddit{Pokemongiveaway},
\subreddit{ACTrade}, and
\subreddit{SVExchange}).  
These communities tended to have highly conventionalized ways negotiating trades
and coordinating meetups.
%Why was the model where the community information was incorporated before
%the LSTM able to take better advantage of it for these communities in particular? 
It would be interesting to investigate these differences further in future work, since it
could reveal differences in the kind of linguistic variation the
different model architectures capture.

@@

\paragraph{Subjective analysis}
In the qualitative discussion offered in \cref{sec:storytelling},
our comparative characterization of the topic, mode of interaction, 
and language varieties
used in the pairs of communities were formed by reading comments from the data our 
language models were trained on. This included Googling words and phrases that 
were unfamiliar. 
Where we make claims about the how the community is ``premised'' or what kinds of 
members it is ``geared towards'' or ``intended for'', these are based on the text
of the sidebar on the community's Reddit page.
While we believe this methodology, aggregated over many pairs of communities, 
is appropriate for making a qualitative comparison
of the community features encoded by different representations, 
to make conclusions about \emph{particular} communities based on such a cursory and
subjective analysis would be dubious and potentially harmful.

\bibliography{paper}
\bibliographystyle{acl_natbib}

>>>>

\begin{document}

\maketitle
\begin{abstract}
Community-level linguistic variation is a core concept in sociolinguistics. In this paper, we use conditioned neural language models to learn vector representations for 510 online communities. We use these representations to measure linguistic variation between communities and investigate the degree to which linguistic variation corresponds with social connections between communities. We find that our sociolinguistic embeddings are highly correlated with a social network-based representation that does not use any linguistic input.
\end{abstract}

@@

Variation is an important object of study in sociolinguistics,
and is naturally amenable to computational analysis \citep{Nguyen2016}.
Most previous computational work on linguistic variation 
has considered variation at the level of macro-social categories, such as gender
\citep{Burger2011,Ciot2013,Bamman2014}, age \citep{Nguyen2013}, and
geographic location \citep{Eisenstein2010,Bamman2014a}.%
In the present work, however, we investigate linguistic variation
across online communities in the social media website Reddit.

@@

For this purpose, we introduce (\cref{sec:cclm}) various
Community-Conditioned Language Models (CCLMs for short). These models
are conditioned on a vector representation (or embedding), which
varies by community. Hence, they learn \emph{community
  embeddings}.  
We report which architectures make best use
of the community information (\cref{sec:performance}), 
however our our primary purpose is not to improve language models in
terms of perplexity, but rather to extract 
community embeddings that capture linguistic similarities between
communities and test how the resulting embeddings
correspond to the social structure of subreddits. To that end, we test
the how well the community embeddings correlate with a social network-based representation of
communities (\cref{sec:embedding-analysis}).

The contributions of this work are twofold. 
First, we develop a language model-based
community embedding that we show is correlated with (but still different from) 
an embedding based on community membership alone.
Second, the method we describe for testing the correlation between two embeddings
from different models is, to our knowledge, novel to computational linguistics.

@@

We experiment with two kinds of model architecture: simple
unidirectional LSTM \citep{Hochreiter1997} and a masked Transformer
\citep{Vaswani2017}. Although Transformer-based language models are considered
state-of-the-art, they achieve dominance partly thanks to the
availability of very large data sets \citep[e.g.,][]{Devlin2019,Brown2020},
which are not available to us.\footnote{Fine-tuning existing models
  is not compatible with our methodology, because we fundamentally
  change the structure of the network by concatenating
  community embeddings with hidden states at various levels.} Thus the LSTM is a worthy model to test for us.

@@

In the CCLMs, we add a \emph{community embedding} parameter, 
which varies depending on the community of origin of the input sample. 
This parameter is concatenated (at each time step) with the hidden layer of the
sequence encoder, at some layer $l_c \leq n$, and passed through a
linear layer which projects the resulting vector back to the original
hidden layer size.  For $l_c = n$, the output of this linear layer is
passed directly to the softmax function, just as the final hidden
layer of the sequence encoder is in other models.  For $l_c=0$, the
community embedding is concatenated with the token embedding.  For
this reason, we set the hidden size of the sequence encoder and the
size of the token embedding to be equal for all models.

@@

Models used a vocabulary of \num{40000} tokens (including a special
out-of-vocabulary token), consisting of the most frequent tokens
across all communities.

We trained the models on a simple 
auto-regressive language modeling task with cross-entropy loss.  Because
the Transformer operates on all tokens in the sequence at once, the
inputs to the model were masked and incrementally un-masked.
We used the AdamW
\citep{Loshchilov2019} optimisation algorithm, with an initial
learning rate of \num{0.001} and no extra control on the decay
of learning rate.
%
The batch size was \num{256} and the maximum sequence length set to
\num{64} tokens, truncating longer messages (16.8\% of messages were
longer than \num{64} tokens).  During training, a dropout rate of
$0.1$ was applied between encoder layers and after each linear layer.

All experiments use models with \num{3} encoder layers,
each with hidden (and token embedding) size of \num{256}. 
The Transformer models had \num{8} attention heads per layer.\footnote{
  This number of attention heads was chosen to give the LSTM and Transformer
  models a comparable number of parameters 
  (\num{22171203} and \num{21779523}, respectively).}
The conditional models were given a community embedding with \num{16} dimensions. 
We experimented with every possible value for $l_c$ in a three-layer model ($l_c\in\{0,1,2,3\}$).

@@

\section{CCLM Performance}\label{sec:performance}

@@

We also consider the average information gain per token of the CCLM over its baseline
un-conditioned counterpart, with the same sequence encoder architecture.
For a given message, information gain is defined as the difference
between the cross-entropy of the unconditioned model and the conditioned model:
\[H_{\mathrm{LM}}(m) - H_{\mathrm{CCLM}}(m)\]
For a set of messages, $M$, we consider the average information gain
in exponential space (as a ratio of perplexities):
\[\IG_M = \frac{e^{\avg_{m \in M}(H_{\mathrm{LM}}(m))}}{e^{\avg_{m \in M}(H_{\mathrm{CCLM}}(m))}}\]
\[\IG_M = {e^{\avg_{m \in M}(H_{\mathrm{LM}}(m) - H_{\mathrm{CCLM}}(m))}}\]
%
Unsurprisingly, the conditioned models mostly have lower perplexity 
than their respective unconditioned baseline models, 
(i.e., $\IG_M > 1$, \cref{tab:model-results}).
While the absolute performance ($\Ppl_{M}$) of the LSTM models is better,
the best Transformer models have somewhat higher information gain
than their LSTM counterparts.

The effect of $l_c$, the depth of the community embedding,
is also different across architectures.
For the LSTM encoder, 
the best model concatenates the community embedding after the first encoder layer ($l_c=1$),
but all of the conditioned models perform similarly well.
For the Transformer, the best model incorporates the community information
first, concatenating it directly to the word vectors ($l_c=0$).
It performs similarly to the model that only integrates the community information
after all all the Transformer layers ($l_c=3$),
but the two middle-layer models actually perform worse than the unconditioned model
(with $\IG_M < 1$).

%We additionally observe that the best LSTM model achieves better
%performance than the best Transformer model. 
%This partly contradicts
%the fact that Transformer-based models are the ones used in
%state-of-the art models for mainstream tasks. 
%We propose that the
%cause is that we are training all models from scratch on a relatively
%small dataset. In this situation, the relatively smaller number of
%parameters of the LSTM means that it can generalise better than the
%Transformer.

@@

We also consider performance stratified by community; that is,
$\Ppl_{M_j}$ and $\IG_{M_j}$, 
where $M_j$ is the set of messages originating from community $c_j$ 
(\cref{fig:comm-stratified-box}).
We observe a lot of variation in baseline perplexity
across communities, with $\Ppl_{M_j}$ ranging from \num{3.67} to
\num{93.58} for the best conditional LSTM model 
(\cref{fig:comm-stratified-box}; also see \cref{sec:community-level-results} for detailed community-level results). 
The conditioned models also perform differently across different communities---%
even among the best models, some communities have $\IG_{M_j} < 1$,
meaning that the CCLM performs worse than the unconditioned baseline for 
messages from that community.
For other communities $\IG_{M_j}$ is much higher, meaning that the CCLM performs better  
(\cref{fig:comm-stratified-box}).\footnote{
  Some of the communities with consistently high $IG_{M_j}$ 
  across all models are primarily non-English, 
  but surprisingly, not the three most extreme
  outliers. There are \subreddit{counting}, \subreddit{friendsafari}, and \subreddit{Fireteams}, 
  the later two of which are places where people coordinate to play video games
  together. The messages in these communites adhere to highly regular formats, 
  which are presumably conventional to the community.}
%
%The variation in information gain across communities is not 
%related to perplexity, however (\cref{fig:ppl-info-gain}).

@@

In this section we investigate the degree to which CCLM community
embeddings correlate with the social network structure of Reddit.

To this end, we compare the CCLM-learned community
embeddings\footnote{
  In this section, we only consider the embeddings from 
  the \emph{best} (highest information gain) CCLM from each architecture family; 
  that is, the LSTM with $l_c=1$ and the Transformer with $l_c=0$, however we
  observed similar results for other values of $l_c$.}
with the community embedding created by \citet{Kumar2018},\footnote{
  Available at \url{https://snap.stanford.edu/data/web-RedditEmbeddings.html}}
which were generated using using a negative-sampling optimization
algorithm, with the author-community co-occurrence matrix as ground
truth, using data from January 2014 to April 2017.
We refer the reader
to \citet{Kumar2018}
for details, but the important point is that no linguistic
information is used to create these embeddings: they only reflect the social
relationship between communities via community membership. 
In contrast, CCLM community embeddings depend in no
way on which user is the author of any given message: we only use the
contents of messages, not authorship data.
%

@@

We consider communities from three different selection criteria: 
Those with high linguistic \emph{and} social similarity 
(where the sum of the two is highest),
those with high linguistic and low social similarity
(where social similarity is below the median and linguistic similarity is highest), and
those with low linguistic and high social similarity
(where linguistic similarity is below these median and linguistic similarity is highest).\footnote{We use the LSTM ($l_c=1$) community vectors for these purposes, 
  but results attain with the best Transformer model.}\footnote{Median similarity
  among pairs of communities was \num{0.177} for the social embedding
  and \num{0.010} and \num{0.012} for the LSTM and Transformer
  linguistic embeddings, respectively.}
We do not consider pairs of communities that are different in both ways,
since these don't offer much in the way of understanding the respective embeddings.

Unsuprisingly, the first category (\cref{fig:embedding-differences-examples}, left) yields communities that are qualitatively very similar. 
The \subreddit{SSBPM} and \subreddit{darksouls} communities are focused
around discussion of a particular videogame, and are paired
with communities that discuss a variation of the same game.
The \subreddit{amiugly} and \subreddit{Rateme} communities are both 
forums where the posts are selfies and the comments are mostly 
comments on the person's appearance.
The two communities paired with \subreddit{reddevils} are 
likewise comprised of fans of a particular English football club.
%That the three football club communities are so closely related points
%to an important point about the social embedding: because of the way
%it was trained, it does not have to be the case that communities with
%a similar representation have a high overlap in membership,
%but rather that members from the first community look similar
%to members from the second community in terms of their \emph{overall}
%community membership profile.

@@

The analysis shows positive correlation for both the LSTM ($r=0.438$)
and Transformer ($r=0.452$) linguistic embeddings.\footnote{ By
  comparison, the correlation between the two linguistic embeddings is
  \num{0.759}.}  The correlations are significant with $p<0.001$ in
all cases.  However, we note that the number of pairs grows with the
square of the number of communities (with 510 communities, we have
129795) pairs), meaning that standard statistical tests on Pearson
correlation will assure us of statistical significance in all but the
weakest of correlations. A further flaw is that the data points in
\(C\) are \emph{not} distributed independently---far from it in fact,
since each data point is generated from \num{2} of \num{510}
independent variables. We consider this last flaw fatal, and take a
different approach for computing the correlation between community
embeddings in the next section.

@@

Perhaps the most topically methodologically similar work to ours 
is that of \citet{DelTredici2017}, who use a modified
skip-gram model to show that lexical semantic variation occurs even across 
different communities organised around the same topic.
Their approach does not result in community level representations, however.

There are several other recent studies that aim to measure \emph{linguistic distinctiveness}
at the level of speech community \citep{OConnor2010,Zhang2018,Lucy2021}.
Distinctiveness is one possible interpretation of the community-stratified information gain 
of the CCLM over its unconditioned counterpart (\cref{sec:ig}). 
Whereas the metrics in previous work are based on lexical frequency
(and in the case of \citet{Lucy2021}, word sense distributions),
CCLM information gain is capable of capturing 
distinctiveness at multiple levels of linguistic analysis. 
However, further work is needed to
investigate exactly what kinds of variation are captured.

@@

For LSTM models, the perplexity per word, averaged over
messages from all communities, was between \num{66.01} and \num{66.35}
(with \num{68.74} for the unconditioned model).
For Transformer models, it varies a bit more, between \num{75.66} and \num{83.53},
but this seems to be mainly due to the poor performance of the models where
the community embedding is inserted between Transformer layers
($l_c=2$ and $3$ both test above the unconditioned Transformer's 
average perplexity of \num{79.13}).
%This could be due to the community embedding and linear layers
%interrupting the delicate layer normalisation between transformer encoder layers.

The pattern of information gain by community is similar across
architectures;  communities that benefit most from the conditioned
model behave that way for both the LSTM and Transformer.  However,
there are some differences.  For example, many of the communities with the biggest 
difference in information gain between the $l_c=0$ and $l_c=3$ LSTMs 
are organised around trading collectables or organising virtual meetups
(e.g.,
%\subreddit{friendsafari},
%\subreddit{Fireteams},
%\subreddit{RandomActsOfGaming},
%\subreddit{randomactsofcsgo},
\subreddit{Pokemongiveaway},
\subreddit{ACTrade}, and
\subreddit{SVExchange}).  
These communities tended to have highly conventionalized ways negotiating trades
and coordinating meetups.
%Why was the model where the community information was incorporated before
%the LSTM able to take better advantage of it for these communities in particular? 
It would be interesting to investigate these differences further in future work, since it
could reveal differences in the kind of linguistic variation the
different model architectures capture.

@@

\paragraph{Subjective analysis}
In the qualitative discussion offered in \cref{sec:storytelling},
our comparative characterization of the topic, mode of interaction, 
and language varieties
used in the pairs of communities were formed by reading comments from the data our 
language models were trained on. This included Googling words and phrases that 
were unfamiliar. 
Where we make claims about the how the community is ``premised'' or what kinds of 
members it is ``geared towards'' or ``intended for'', these are based on the text
of the sidebar on the community's Reddit page.
While we believe this methodology, aggregated over many pairs of communities, 
is appropriate for making a qualitative comparison
of the community features encoded by different representations, 
to make conclusions about \emph{particular} communities based on such 
an analysis would be dubious and potentially harmful.

\bibliography{paper}
